%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Ghassen Bargougui - Senior Java Engineer (CRM/BSS)  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume}

\begin{document}

% --------- Contact Information -----------

\introduction[
fullname={Ghassen Bargougui},
address={Fukuoka, Japan},
email={ghassen.brg16@gmail.com},
phone={+81 70 8502 9039},
linkedin={linkedin.com/in/ghassenbrg}
]

% --------- Summary -----------

\summary{
Application Engineer with 6+ years of experience building and modernizing scalable enterprise systems, currently contributing to fintech platforms supporting 25M+ users in Japan. Strong in Java (Spring Boot, MicroProfile), microservices, and API architecture, with full-stack experience in Angular and Vue/Nuxt. Hands-on in hybrid cloud transformation, Kubernetes, and CI/CD automation, with a focus on clean architecture and resilient, high-performance systems. Oracle Certified Java SE 11 Developer. Fluent in English and French, Arabic (native), with basic Japanese.
}

% --------- Education ---------

\begin{educationSection}{Education}
\educationItem[
university={ESPRIT (Private Higher School of Engineering and Technology), Tunis, Tunisia},
graduation={July 2023},
program={Engineer’s Degree, Software Engineering}
]
\educationItem[
university={ISIMM (Higher Institute of Computer Science and Mathematics), Monastir, Tunisia},
graduation={June 2019},
program={Bachelor’s Degree, Computer Science}
]
\end{educationSection}

% --------- Skills -----------

\begin{skillsSection}{Technical Skills}
\skillItem[
category={Programming Languages},
skills={Java, TypeScript, SQL, JavaScript, HTML5, CSS3}
] \\
\skillItem[
category={Frameworks \& Libraries},
skills={Spring Boot, MicroProfile, Jakarta EE (Java EE), Hibernate, JPA, Angular, Vue.js, Nuxt.js, PrimeNG, JUnit, Camunda BPM, NestJS, Node.js}
] \\
\skillItem[
category={API \& Microservices},
skills={RESTful API Design, OpenAPI, Spring Cloud, ActiveMQ}
] \\
\skillItem[
category={Databases},
skills={PostgreSQL, MySQL, Oracle (PL/SQL), MongoDB}
] \\
\skillItem[
category={DevOps \& Tools},
skills={Docker, Kubernetes, Jenkins, GitLab CI/CD, Maven, Git, Nginx, WildFly, Tomcat, AWS, GCP, JProfiler, SonarQube, Linux, Jira, Confluence}
] \\
\skillItem[
category={Security},
skills={Keycloak (OAuth2, OIDC, JWT), Linux Server Management}
]
\end{skillsSection}

% --------- Experience -----------

\begin{experienceSection}{Professional Experience}

\experienceItem[
company={Rakuten},
location={Fukuoka, Japan},
position={Application Engineer},
duration={Dec 2025 – Present}
]
\begin{itemize}
\itemsep -6pt {}
\item Member of the Technology Incubation Team, contributing to architecture design, modernization, and cloud transformation of Rakuten Card core systems.
\item Design, develop, and maintain backend services for large-scale card payment and credit management platforms.
\item Develop private and public APIs for secure, efficient integration across internal and customer-facing applications.
\item Contribute to modernization initiatives across legacy and new systems, including transition from Java-based applications to modern JavaScript/SSR-based architectures.
\item Contribute to a hybrid cloud migration program from on-premise to Google Cloud Platform (GCP), including cloud-native refactoring, CI/CD implementation, and containerized deployment strategies.
\item Conduct code reviews, promote engineering best practices, and collaborate closely with Product Owners and cross-functional teams.
\end{itemize}

\experienceItem[
company={Sogeti (on mission at BGL BNP Paribas)},
location={Luxembourg},
position={Software Engineer},
duration={Feb 2025 – Nov 2025}
]
\begin{itemize}
\itemsep -6pt {}
\item Developed and maintained internal banking applications using Java (Spring Boot, Hibernate), Angular, and PostgreSQL/Oracle, with strong focus on security and performance.
\item Built and optimized RESTful APIs and contributed to the design of microservices, ensuring clean service boundaries and robust integration with internal and external systems.
\item Participated in architectural and system design discussions with architects and cross-functional teams, helping to align solutions with enterprise standards and business requirements.
\end{itemize}

\experienceItem[
company={CBTW},
location={Luxembourg},
position={Java Full-Stack Developer},
duration={Sept 2024 – Jan 2025}
]
\begin{itemize}
\itemsep -6pt {}
\item Designed and developed microservices architectures, migrating legacy monolithic components to modular, independently deployable services using Spring Boot, Angular, and PostgreSQL.
\item Engineered RESTful APIs for seamless integration between backend services and external systems, applying best practices for API versioning, security, and documentation.
\item Refactored monolithic components into microservices, improving scalability and maintainability.
\item Automated application deployment with Jenkins \& Docker, reducing manual release efforts.
\end{itemize}

\experienceItem[
company={VERMEG for Banking and Insurance},
location={Tunis, Tunisia},
duration={Oct 2019 – Aug 2024}
]

\positionItem[
position={Analyst Software Engineer},
duration={Jan 2023 – Aug 2024}
]
\begin{itemize}
\itemsep -6pt {}
\item Owned core backend components and served as primary contact for cross-team design clarifications, supporting integration and solution delivery.
\item Collaborated with business, architects, and framework teams in requirements analysis and solution design, ensuring scalable and maintainable microservices and API contracts.
\item Produced UML and sequence diagrams to document system designs and support technical decision-making.
\item Proposed and validated technical solutions for client requirements, supporting colleagues and facilitating cross-team alignment.
\end{itemize}

\positionItem[
position={Software Engineer},
duration={Oct 2019 – Dec 2022}
]
\begin{itemize}
\itemsep -6pt {}
\item Led backend engineering efforts for multiple high-traffic insurance \& financial applications.
\item Designed and optimized high-volume transactional APIs, ensuring high availability and performance.
\item Implemented Keycloak-based authentication \& RBAC, improving access security.
\item Reduced API response time by 50\% through query optimization and caching strategies.
\item Built automated workflows using ActiveMQ for bulk processing, increasing efficiency by 40\%.
\end{itemize}

\end{experienceSection}

% --------- Projects -----------

\begin{experienceSection}{Key Projects}

\projectItem[
title={BGL BNP Paribas Mandate Management (Full-Stack Engineer)},
duration={2025 – Present},
keyHighlight=Developing mandate management features for banking systems in a fully Agile tribe and squad.
]
\begin{itemize}
\itemsep -6pt {}
\item Deliver end-to-end solutions for customer mandate management using Spring Boot (including batch processing) and Angular with Angular Material.
\item Ensure high code quality and robust unit testing, leveraging SonarQube for static analysis and compliance.
\item Automate build and deployment pipelines with Maven, Git, and Jenkins.
\item Collaborate cross-functionally within a fast-paced Agile environment, participating in all ceremonies and code reviews.
\end{itemize}

\projectItem[
title={SalesFlow (Lead Developer)},
duration={2023 – 2024},
keyHighlight=Led migration to Camunda BPM-based architecture, reducing manual processes by 30\%.
]
\begin{itemize}
\itemsep -6pt {}
\item Conducted functional analysis and client workshops to refine business requirements.
\item Designed and developed high-performance REST APIs and scalable microservices.
\item Implemented a multi-threaded batch processing system, optimizing large insurance transactions.
\item Integrated ActiveMQ for bulk processing, increasing transaction speed by 40\%.
\end{itemize}

\projectItem[
title={PackManager (Backend Developer)},
duration={2022 – 2023},
keyHighlight=Developed a configuration platform for insurance products, streamlining offer creation.
]
\begin{itemize}
\itemsep -6pt {}
\item Analyzed client requirements and developed UML models.
\item Designed and optimized RESTful APIs for flexible insurance product customization.
\item Refactored legacy code to improve maintainability and reduce technical debt.
\item Improved system execution using JProfiler, enhancing response time by 35\%.
\end{itemize}

\projectItem[
title={Insurance Pricing Module (Full-Stack Developer)},
duration={2020 – 2021},
keyHighlight=Led functional analysis and actuarial feature development in Java.
]
\begin{itemize}
\itemsep -6pt {}
\item Designed and implemented features for insurance product configuration and premium calculation.
\item Developed actuarial functions in Java with unit testing.
\item Optimized data integration and pricing configuration testing with Apache POI.
\end{itemize}

\end{experienceSection}

% --------- Certifications -----------

\begin{skillsSection}{Certifications}
\skillItem[
category={Oracle},
skills={Oracle Certified Professional, Java SE 11 Developer (Sept 2022) -- Certification Badge: bit.ly/ocp11gb}
]
\end{skillsSection}

% --------- Languages -----------

\begin{skillsSection}{Languages}
\skillItem[
category={Arabic},
skills={Native}
] \\
\skillItem[
category={English},
skills={Fluent}
] \\
\skillItem[
category={French},
skills={Fluent}
] \\
\skillItem[
category={Japanese},
skills={Basic}
]
\end{skillsSection}

\end{document}
